From Questions to Queries -- Enhancing the Curt System by a Theory and Implementation of Embedded WH-Questions

### 2008-07-29 thesis/paper.tex
added more outlines.

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{bbm,qtree,natbib,stmaryrd,aleks,linguex}

\newcommand{\abbr}{\textsf}
\newcommand{\pn}{\textsc}
\newcommand{\url}[1]{\texttt{http://#1}}
%names
\newcommand{\curt}{\pn{Curt}}
\newcommand{\prol}{\pn{Prolog}}

@@

\subsection{General Comparison of the Curt System}

@@

@@

\subsection{Modality and Possible Worlds}
\label{sec:indices}
\subsection{Treatment of Baker-Ambiguities}

>>>>

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{bbm,qtree,natbib,stmaryrd,amsmath,amssymb,aleks,linguex}

\newcommand{\abbr}{\textsf}
\newcommand{\pn}{\textsc}
\newcommand{\url}[1]{\texttt{http://#1}}
%names
\newcommand{\curt}{\pn{Curt}}
\newcommand{\prol}{\pn{Prolog} }

@@

\pn{Curt}, a system written in \prol that is able to interpret basic utterances
in natural language and express them in terms of first order logic, is developed
throughout chapter six of \cite{blackburnbos:cl1}. While relatively simple in
terms of lexical and grammatical coverage it is able to perform basic checks for 
\emph{consistency} and \emph{informativity} of its input\footnotemark, within
the bounds of the tools it uses.

\footnotetext{Here, the notion of \emph{consistency} is meant as \emph{validity}
of the input and \emph{informativity} denotes \emph{validity}. Thus, if
$\mathcal{D}$, the discourse so far and $\phi$ a new input token (fully parsed
sentence), then consistency means $\mathcal{D} \to \phi$ holds and informativity
means $\mathcal{D} \nvDash \phi$.}
\subsection{General Comparison of the Curt System}

@@

We first derive know(john,all(X,imp(woman(X),love(X,john)))) from the syntax of
john knows whether every woman loves john, then we see if
all(X,imp(woman(X),love(X,john))) is valid (uninformative) and ridicule John, if
it's not valid and not consistent, assert his knowledge of the fact that it's
not true. If it's true, we assert he knows that.

For whether we can ridicule him if it's not true (inconsistent).
\newcommand{\discourse}{\ensuremath{\mathcal{D}}}
The MB/TP do a comparison \discourse to all(X,imp(woman(X),love(X,john)))

@@

\subsection{Modality and Possible Worlds}
\label{sec:indices}

We have seen that some embedding verbs may not be interpreted without
implementing a higher order formalism that is able to model the notion of
\emph{possible} and \emph{accessible} worlds. While foobar %fixme! Nelken &
% Francez 2001
argue for an extensional treatment of questions, they already % n & f 2006
retract their claims and admit that a ``minimal account of intensionality'' has
to be assumed. While they propose a two-world system later adopted in
\cite{g:is}, this is not going to suffice if we want to model each individual's
knowledge in order to be able to discriminate people's knowledge and beliefs.
%fixme bla bla

\subsection{Treatment of Baker-Ambiguities}

\subsection{Alternative Questions -- Inquisitive Semantics}

\cite{g:is} presents a novel approach to treating questions in natural
semantics: \pn{Inquisitive Semantics}. Groenendijk presents a new logic
formalism aimed at providing a wider coverage of the intentions of question in
human language. The main source of the ``inquisitiveness'' of statements is
given by the interpretation of \emph{disjunction}. We will now show how to
incorporate this novel approach into the \pn{Curt} system.

We will, however depart from the path we have been following throughout this
paper and first implement a theory for direct questions. Only then will we extend
it to also cover embedded alternative questions.
